Using physics simulations to predict children's and adults' preference for physical interactions

### 2021-02-04 paper/paper2021.Rmd
small edits

## Comparison of Children's vs. Adults' Preferences
\vspace{-4pt}
Finally, we compared the trial-level preferences of children and adults.
Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type. 
(visualizing the same data presented in Table 2).
If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task and suggests some consistency in the trial-level effects across development. 
This consistency also confers additional motivation for attempting to understand what drives human interest in particular physical interactions in this task through computational models.

@@

Examination of the fitted model preferences revealed that none of them achieved a good fit to human preferences.
For example, while the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, but explained no trial-level variation and was in fact negatively correlated with people's choices, overall.
Thus, instead of reporting predictions from fitted $\beta$s for each feature, we show in Table 2 the correlation between model preferences (with softmax $\beta = 1$) vs. adults' and children's choice proportions, both to all trials and separately for containment and support trials.
The feature with the strongest correlation to adults is *Vel(Target)* ($r=.33$), but adults' support trials were more correlated with *1/SD(Target Pos)* ($r=.39$), while containment trials were most correlated with *Vel(Drop Obj)* ($r=.54$).
The feature with the strongest correlation to children is *Supp. Sharpness* ($r=.18$), but like adults, children's support trial choices were better correlated with *1/SD(Target Pos)* ($r=.41$).
Children's containment trial choices were most correlated with *Max(Target Dist)* ($r=.43$), but *Vel(Drop Object)*, the most related to adults' containment trials, was not far behind ($r=.41$).
Many of the other features show weak or even moderate negative correlations with people's choices.

@@

# combine all_trials, supp_trials, and cont_trials
mod_tab <- all_trials %>% select(-mse) %>%
  rename(`All` = r) %>% 
  left_join(supp_trials) %>%
  left_join(cont_trials) %>%
  filter(is.element(feature, described_features)) %>%
  arrange(desc(`All`), feature)  %>%
  mutate(Age = ifelse(Age=="children", "Child:", "Adult:")) %>%
  pivot_wider(names_from=Age, values_from=c(`All`, `Support`, `Contain`), 
              names_glue = "{Age} {.value}") %>%
  arrange(desc(`Adult: All`)) %>%
  mutate(feature = case_when(feature == 'support_response_sharpness_C=1' ~ 'Supp. Sharpness',
                             feature == 'support_probability' ~ 'Pr(support)',
                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'Vel(Target)',
                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'Vel(Drop Obj)',
                             feature == 'avg_len' ~ 'M(Move Time)',
                             feature == 'len_std' ~ 'SD(Move Time)',
                             feature == 'obj_final_position_invstd_objects=target' ~ '1/SD(Target Pos)',
                             feature == 'obj_final_position_invstd_objects=drop' ~ '1/SD(Drop Obj Pos)',
                             feature == 'avg_final_radius_objects=target' ~ 'M(Target Dist)',
                             feature == 'avg_final_radius_objects=drop' ~ 'M(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=drop' ~ 'Max(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=target' ~ 'Max(Target Dist)',
                             TRUE ~ feature))

>>>>

## Comparison of Children's vs. Adults' Preferences
\vspace{-4pt}
Finally, we compared the trial-level preferences of children and adults.
Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2, but with 95% CIs).
If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task as well as suggesting some consistency in the trial-level effects across development. 
This consistency also confers additional motivation for attempting to understand what drives human interest in particular physical interactions in this task through computational models.

@@

Examination of the fitted model preferences revealed that none of them achieved a good fit to human preferences.
For example, while the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained no trial-level variation and was in fact negatively correlated with people's choices.
Thus, instead of reporting predictions from fitted $\beta$s for each feature, we show in Table 2 the correlation between model preferences (with softmax $\beta = 1$) vs. adults' and children's choice proportions, both to all trials and separately for containment and support trials.
The feature with the strongest correlation to adults is *Vel(Target)* ($r=.33$), but adults' support trials were more correlated with *1/SD(Target Pos)* ($r=.39$), while containment trials were most correlated with *Vel(Drop Obj)* ($r=.54$).
The feature with the strongest correlation to children is *Supp. Sharpness* ($r=.18$), but like adults, children's support trial choices were better correlated with *1/SD(Target Pos)* ($r=.41$).
Children's containment trial choices were most correlated with *Max(Target Dist)* ($r=.43$), but *Vel(Drop Object)*, the most related to adults' containment trials, was not far behind ($r=.41$).
Many of the other features show weak or even moderate negative correlations with people's choices.

@@

# combine all_trials, supp_trials, and cont_trials
mod_tab <- all_trials %>% select(-mse) %>%
  rename(`All` = r) %>% 
  left_join(supp_trials) %>%
  left_join(cont_trials) %>%
  filter(is.element(feature, described_features)) %>%
  arrange(desc(`All`), feature)  %>%
  mutate(Age = ifelse(Age=="children", "Child:", "Adult:")) %>%
  pivot_wider(names_from=Age, values_from=c(`All`, `Support`, `Contain`), 
              names_glue = "{Age} {.value}") %>%
  arrange(desc(`Adult: All`)) %>%
  mutate(feature = case_when(feature == 'support_response_sharpness_C=1' ~ 'Supp. Sharpness',
                             feature == 'support_probability' ~ 'Pr(support)',
                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'Vel(Target)',
                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'Vel(Drop Obj)',
                             feature == 'avg_len' ~ 'M(Move Time)',
                             feature == 'len_std' ~ 'SD(Move Time)',
                             feature == 'obj_final_position_invstd_objects=target' ~ '1/SD(Target Pos)',
                             feature == 'obj_final_position_invstd_objects=drop' ~ '1/SD(Drop Obj Pos)',
                             feature == 'avg_final_radius_objects=target' ~ 'M(Target Dist)',
                             feature == 'avg_final_radius_objects=drop' ~ 'M(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=drop' ~ 'Max(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=target' ~ 'Max(Target Dist)',
                             TRUE ~ feature)) %>%
  rename(Feature = feature)
